The Gillespie Algorithm: Stochastic Modeling of Molecular Reaction Networks

### 2024-11-24 paper.Rmd
updated introduction and references

This is an R Markdown document. Markdown is a simple formatting syntax
for authoring HTML, PDF, and MS Word documents. For more details on
using R Markdown see <http://rmarkdown.rstudio.com>. We analysis the data in R(@citeR).

The rest of this project is as follows. In Section 2, we review some
basic concepts. In Section 3, we introduce the topic. In Section 4, we
have an application and simualtion. Section 5 provides conclusion and
some closing remarks.

>>>>

The Gillespie Algorithm was presented in 1976 by Daniel T. Gillespie (@Gillespie1976). This algorithm was developed  to answer the question, “If a fixed volume V contains a spatially uniform mixture of N chemical species which can inter-react through M specified chemical reaction channels, then given the numbers of molecules of each species present at some initial time, what will these molecular population levels be at any later time?” (@Gillespie1977). Given the trajectory of this molecular reaction is a stochastic process, this algorithm can simulate various molecular equation systems, such as radioactive decay models or decaying-dimerization reaction sets (@GillespieSSA).

In the following report, we will review basic concepts of the Gillespie Algorithm (Section 2), then we will present the theory of the Gillespie Algorithm (Section 3). Afterwards, we will demonstrate a stochastic simulation using the Gillespie algorithm of a dimerization reaction set (Section 4), using R(@citeR). Finally, we will provide our concluding remarks (Section 5).
